Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-21 edubots_surveys.Rnw
Discuss Rq4

Regarding Gender grouping, both gender agree in their uses, so it seems not relevant at all. When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational High School teachers. This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform. Furthermore, the high student/teacher ratios that university docents have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs. This could ameliorate the number of misunderstandings and email overload that so many students might generate.

@@

>>>>

Regarding gender grouping, both genders agree in their uses, so it seems not relevant at all. When looking at the plot containing the sector differentiation it is interesting ot observe how university teachers prefer in a higher proportion to use them for grades and FAQs in comparison with Vocational High School teachers. This seems reasonable as the frequency of seeing the students is smaller at the University so, automating the grade notification for continuous evaluation could seem much more comfortable using an automated tool than using the traditional platform. Furthermore, the high student/teacher ratios that university docents have to deal with could be another reason to have a higher number of them willing to use chatbots for FAQs. This could ameliorate the number of misunderstandings and email overload that so many students might generate.

@@

An analysis of survey questions related to RQ4 seems to indicate that teachers prefer to have interaction with their students in a chat "room"; a preference of {\em horizontal} interaction might indicate the need to delegate or offload part of the burden of answering, and attending, every single question posed by students. In an horizontal setting, other students can answer if the teacher does not do it immediately. This might also be the reason why the possibility of using tools from which analytics can be extracted is also valued by teachers: that way, activity in the chat tool, answering questions, regularity, can all be observed and valued as part of the process of assesing achievement of learning objectives by students.
